Interval Probability for Fuzzy Quantum Theories

### 2016-08-04 prob.tex
prob.tex Updates...

% \begin{example}{[}Two-coin probability space with finite set-valued
% probability measure{]} \label{ex2} Under the new set-valued requirement,
% the probability measure in the first example becomes: 
% \[
% \begin{array}{c@{\qquad\qquad}c}
% \begin{array}{rcl}
% \pmeas(\emptyset) & = & \imposs\\
% \pmeas(\{HH\}) & = & \poss\\
% \pmeas(\{HT\}) & = & \imposs\\
% \pmeas(\{TH\}) & = & \poss\\
% \pmeas(\{TT\}) & = & \imposs\\
% \pmeas(\{HH,HT\}) & = & \poss\\
% \pmeas(\{HH,TH\}) & = & \poss\\
% \pmeas(\{HH,TT\}) & = & \poss
% \end{array} & \begin{array}{rcl}
% \pmeas(\{HT,TH\}) & = & \poss\\
% \pmeas(\{HT,TT\}) & = & \imposs\\
% \pmeas(\{TH,TT\}) & = & \poss\\
% \pmeas(\{HH,HT,TH\}) & = & \poss\\
% \pmeas(\{HH,HT,TT\}) & = & \poss\\
% \pmeas(\{HH,TH,TT\}) & = & \poss\\
% \pmeas(\{HT,TH,TT\}) & = & \poss\\
% \pmeas(\{HH,HT,TH,TT\}) & = & \poss
% \end{array}\end{array}
% \]
% Despite the fact that we have lost all numeric information, the probability
% measure still reveals that the second coin is double-headed. We have
% however lost the information regarding the bias in the first coin.
% This information can be recovered with a more refined probability
% measure as we show next. \qed\end{example}

@@

% \begin{example}\label{Two-coin-set-valued-again}{[}Two-coin probability
% space with set-valued probability measure, again{]} 
% \[
% \begin{array}{c@{\qquad\qquad}c}
% \begin{array}{rcl}
% \pmeas(\emptyset) & = & \imposs\\
% \pmeas(\{HH\}) & = & \unlikely\\
% \pmeas(\{HT\}) & = & \imposs\\
% \pmeas(\{TH\}) & = & \likely\\
% \pmeas(\{TT\}) & = & \imposs\\
% \pmeas(\{HH,HT\}) & = & \unlikely\\
% \pmeas(\{HH,TH\}) & = & \likely\\
% \pmeas(\{HH,TT\}) & = & \unlikely
% \end{array} & \begin{array}{rcl}
% \pmeas(\{HT,TH\}) & = & \likely\\
% \pmeas(\{HT,TT\}) & = & \imposs\\
% \pmeas(\{TH,TT\}) & = & \likely\\
% \pmeas(\{HH,HT,TH\}) & = & \likely\\
% \pmeas(\{HH,HT,TT\}) & = & \unlikely\\
% \pmeas(\{HH,TH,TT\}) & = & \likely\\
% \pmeas(\{HT,TH,TT\}) & = & \likely\\
% \pmeas(\{HH,HT,TH,TT\}) & = & \likely
% \end{array}\end{array}
% \]
% In this example, we can get the information that the first coin is
% weighted and the second coin is double-headed. However, we may notice
% that the set-valued probability of the whole space~$\{HH,HT,TH,TT\}$
% are different between these two examples. This problem can be fixed
% when we moved on to the next section. \qed\end{example}

@@

In contrast to real-valued probability measure, there is no easy Radon-Nikodym
theorem to simplify an interval-valued probability measure to its
Radon-Nikodym derivative. So far the Radon-Nikodym Theorems found
for the interval-valued probability measure are either too restricted
to apply to all interval-valued probability measures~\cite{Choquet1954,Graf1980,Goodman2013}
or corresponding an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
to another set function~$\bar{\rho}:\events\rightarrow\bar{\mathscr{I}}$
which is not as simple as the original Radon-Nikodym derivative~\cite{GilboaSchmeidler1994,Goodman2013}.

Although there is no easy Radon-Nikodym theorem, an interval-valued
probability measure can still be understood by its relation with real-valued
probability measures, like constructing example~\ref{ex3} from example~\ref{ex1}.
In general, this idea can be generalized to the following definition
of core.

@@

\yutsung{Because the physical meaning of convex is still not clear,
it would be better if we can find or prove a theorem which removes
``convex'' in the theorem. However, the literature contradicts to
each other so at least I need to trace an example to see which one
is correct, or neither proved the theorem we want.

@@

On one hand, a combination of the following two theorems show interval-valued
probability measures is likely to have a core.

@@

Verifying the example to see who is right...}

@@

A set of events~$\events$ together with quantum probability measure is called a
\emph{quantum probability space}. 
Comparing to the classical probability space, the empty set~$\emptyset$
corresponds to the empty projection~$\mathbb{0}$ and the event of
whole space~$\Omega$ corresponds to the identity projection~$\mathbb{1}$.
In contrast, the union~$\cup$ of any two events always gives an
event classically, but the operator addition~$\tensor*[_{\mathscr{O}}]{+}{}$
of two projections may not be a projection. As the result, the classical
condition~$\pmeas(E_{1}\cup E_{2})=\pmeas(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\pmeas(E_{2})$
is always defined, and it is true when $E_{1}$ and $E_{2}$ are disjoint;
however, $\mu\left(P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\right)=\mu(P_{1})\tensor*[_{\mathbb{R}}]{+}{}\mu(P_{2})$
is always true whenever the left-handed side is defined.

@@

Moreover, the Born rule can be extended to a mixed state. Suppose
we prepares a set of state~$\ket{\phi_{j}}$ each with probability~$q_{j}$,
the state of the system can be expressed as a density matrix~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$,
where $\sum_{j}q_{j}=1$. It is natural that the quantum probability
measure introduced by $\rho$ is the combination of $\mu_{\phi_{j}}^{B}$
with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
\begin{eqnarray}
\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\mu_{\phi_{j}}^{B}\left(P\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}

@@

Then, the Radon-Nikodym theorem is generalized quantum~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.
If the mixed state~$\rho$ is considered as the Radon-Nikodym derivative
with respect to the trace, we have Gleason's theorem: in Hilbert spaces
of dimension $d\geq3$, given a quantum probability measure $\mu$,
there exist a mixed state~$\rho$ that induces such a measure using
the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
By applying Gleason's theorem, we can extend lemma~\ref{lem:quantumProbabilityMeasure}
to the following corollary.

>>>>

% \begin{example}[Two-coin probability space with finite set-valued
% probability measure] \label{ex2} Under the new set-valued requirement,
% the probability measure in the first example becomes: 
% \[
% \begin{array}{c@{\qquad\qquad}c}
% \begin{array}{rcl}
% \pmeas(\emptyset) & = & \imposs\\
% \pmeas(\{HH\}) & = & \poss\\
% \pmeas(\{HT\}) & = & \imposs\\
% \pmeas(\{TH\}) & = & \poss\\
% \pmeas(\{TT\}) & = & \imposs\\
% \pmeas(\{HH,HT\}) & = & \poss\\
% \pmeas(\{HH,TH\}) & = & \poss\\
% \pmeas(\{HH,TT\}) & = & \poss
% \end{array} & \begin{array}{rcl}
% \pmeas(\{HT,TH\}) & = & \poss\\
% \pmeas(\{HT,TT\}) & = & \imposs\\
% \pmeas(\{TH,TT\}) & = & \poss\\
% \pmeas(\{HH,HT,TH\}) & = & \poss\\
% \pmeas(\{HH,HT,TT\}) & = & \poss\\
% \pmeas(\{HH,TH,TT\}) & = & \poss\\
% \pmeas(\{HT,TH,TT\}) & = & \poss\\
% \pmeas(\{HH,HT,TH,TT\}) & = & \poss
% \end{array}\end{array}
% \]
% Despite the fact that we have lost all numeric information, the probability
% measure still reveals that the second coin is double-headed. We have
% however lost the information regarding the bias in the first coin.
% This information can be recovered with a more refined probability
% measure as we show next. \qed\end{example}

@@

% \begin{example}\label{Two-coin-set-valued-again}[Two-coin probability
% space with set-valued probability measure, again] 
% \[
% \begin{array}{c@{\qquad\qquad}c}
% \begin{array}{rcl}
% \pmeas(\emptyset) & = & \imposs\\
% \pmeas(\{HH\}) & = & \unlikely\\
% \pmeas(\{HT\}) & = & \imposs\\
% \pmeas(\{TH\}) & = & \likely\\
% \pmeas(\{TT\}) & = & \imposs\\
% \pmeas(\{HH,HT\}) & = & \unlikely\\
% \pmeas(\{HH,TH\}) & = & \likely\\
% \pmeas(\{HH,TT\}) & = & \unlikely
% \end{array} & \begin{array}{rcl}
% \pmeas(\{HT,TH\}) & = & \likely\\
% \pmeas(\{HT,TT\}) & = & \imposs\\
% \pmeas(\{TH,TT\}) & = & \likely\\
% \pmeas(\{HH,HT,TH\}) & = & \likely\\
% \pmeas(\{HH,HT,TT\}) & = & \unlikely\\
% \pmeas(\{HH,TH,TT\}) & = & \likely\\
% \pmeas(\{HT,TH,TT\}) & = & \likely\\
% \pmeas(\{HH,HT,TH,TT\}) & = & \likely
% \end{array}\end{array}
% \]
% In this example, we can get the information that the first coin is
% weighted and the second coin is double-headed. However, we may notice
% that the set-valued probability of the whole space~$\{HH,HT,TH,TT\}$
% are different between these two examples. This problem can be fixed
% when we moved on to the next section. \qed\end{example}

@@

In contrast to real-valued probability measures, there is no easy
Radon-Nikodym theorem to simplify an interval-valued probability measure
to its Radon-Nikodym derivative. So far, the interval-valued Radon-Nikodym
Theorems are either too restricted to apply to all interval-valued
probability measures~\cite{Choquet1954,Graf1980,Goodman2013} or
corresponding an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
to another set function~$\bar{\rho}:\events\rightarrow\bar{\mathscr{I}}$
which is not as simple as the original Radon-Nikodym derivative~\cite{GilboaSchmeidler1994,Goodman2013}.

Although there is no easy Radon-Nikodym theorem, an interval-valued
probability measure can still be understood by its relation with real-valued
probability measures. For example, the real-valued probability measure
in example~\ref{ex1} can be used to construct the interval-valued
probability measure in example~\ref{ex3}. Conversely, the interval-valued
probability measure in example~\ref{ex3} could be understood by
the real-valued probability measure and its Radon-Nikodym derivative
in example~\ref{ex1}. The relation between example~\ref{ex1} and
\ref{ex3} can be abstracted into the definition of core.

@@

\yutsung{Because the physical meaning of convex is still not clear,
it would be better if we can find or prove a theorem which removes
``convex'' in the theorem. However, the literature contradicts to
each other so at least I need to trace an example to see which one
is correct, or prove the theorem we want independently...

@@

On one hand, a combination of the following two theorems show every
cloud has a core.

@@

Verifying the example to see who is right... Also need to confirm
whether interval-valued probability measures and clouds are really
the same.}

@@

A set of events~$\events$ together with a quantum probability measure
is called a \emph{quantum probability space}. Comparing to classical
probability spaces, the empty set~$\emptyset$ corresponds to the
empty projection~$\mathbb{0}$, and the event of whole space~$\Omega$
corresponds to the identity projection~$\mathbb{1}$. In contrast,
the union~$\cup$ of any two events always gives an event classically,
but the operator addition~$\tensor*[_{\mathscr{O}}]{+}{}$ of two
projections may not be a projection. As the result, the classical
condition~$\pmeas(E_{1}\cup E_{2})=\pmeas(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\pmeas(E_{2})$
is always defined, and it is true when $E_{1}$ and $E_{2}$ are disjoint;
however, $\mu\left(P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\right)=\mu(P_{1})\tensor*[_{\mathbb{R}}]{+}{}\mu(P_{2})$
is always true whenever the left-handed side is defined.

@@

Moreover, the Born rule can be extended to a mixed state. When we
prepares a state, suppose the probability of preparing state~$\ket{\phi_{j}}$
is $q_{j}$, the state of the system can be expressed as a density
matrix~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$, where $\sum_{j}q_{j}=1$.
Then, the quantum probability measure introduced by $\rho$ is the
combination of $\mu_{\phi_{j}}^{B}$ with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
\begin{eqnarray}
\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\mu_{\phi_{j}}^{B}\left(P\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}

@@

In this sense, the Radon-Nikodym theorem could be generalized to Gleason's
theorem: in quantum~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}:
in Hilbert spaces of dimension $d\geq3$, given a quantum probability
measure $\mu$, there exist a mixed state~$\rho$ that induces such
a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
By applying Gleason's theorem, we can extend lemma~\ref{lem:quantumProbabilityMeasure}
to the following corollary.
